\LARGE \bf Multi-dimensional Optimization of Gasoline-fueled Variable Pitch Multirotor Aircraft

### 2016-03-23 paper.tex
added some background and references stuff

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Background}

Control of variable pitch multirotor aircraft was studied by Cutler \cite{Cutler2012}. There is a variable pitch quad commercially available \cite{stingray2016}.  There are also several hobbyist attempts at gas powered variable pitch quads \cite{diy2016}, \cite{hackaday2016}.

In our knowledge there has been no attempt to use a gas powered variable pitch quad to maximize the flight time for carrying a large payload.

There are many commercially available parts for a gas quad, including motors
